\todo{Something} presents OpenAdcess

### 2017-02-18 aesthetics.tex
there is a house in new orleans not the one you heard about i'm talking bout another house

>>>>

ACM pep rallies: a single academic article will be fired from a cannon but invariably so many people fight over it it just shreds to pieces

ACM vending machines, human-staffed, particularly cruel topple people who stick hand in (or maybe joke about papers being can-shaped so if you try to steal one, you get stuck in the vending machine unless you decide to let go of the can. The Virginia state legislature has approved a measure that would allow tobacco companies to generously contribute to the ACM and the advancement of science (withheld from the wages of 14-year-old tobacco pickers), by furnishing vending machines that sell cigarette packs with snippets of technical papers on them, over the space on the pack where the Surgeon's General Warning used to go. Each vending machine would be affiliated with a particular ACM journal.
